---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Dmitriy Kairbayev"
date: "16 12 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as 
whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

The application include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Using data

Downloading data

data(GaltonFamilies)

## Here, we will use the following libraries:

library(shiny)
library(HistData)
library(dplyr)
library(ggplot2)

```{r}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

## Construction of the plot

We conduct the below scatterplot for the prediction of children height.

```{r}
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight, xlab = "Average Height of the Parents (in inches)", ylab = "Height of the Child (in inches)", main = "Scatterplot of Galton FamilyData", pch = 19, frame.plot = FALSE, col = ifelse(GaltonFamilies$gender == "female", "red", "blue"))
legend(65,80, pch = c(19,19), col = c("red","blue"), c("female", "male"), bty = "o",cex = .8)
```
